KeysarMouseTracking.csv

### 2017-09-27 analysis/cogSci_analysis.Rmd
Add script for reformatting speaker data to notebook

criticalMessagesExp1 <- read.csv("./experiment1/data/processedLabelsExp1.csv") %>%
  left_join(turkerRatings, by = relevantProperties) %>%
  mutate(exp = "Exp.1")
criticalMessagesExp2 <- read.csv("../experiment2/data/processedLabelsExp2.csv") %>%
  left_join(turkerRatings, by = relevantProperties) %>%
  mutate(exp = "Exp.2")

@@

library(binom)

Exp1Errs = itemInequalitiesExp1 %>%
  do(mutate(., errorLower = binom.confint(.$errorCount, .$total, 
                                     method = "bayes")$lower,
               errorUpper = binom.confint(.$errorCount, .$total, 
                                     method = "bayes")$upper)) %>%
  select(objectSet, errorRate, errorLower, errorUpper)

@@

g <- (ggplot(Exp2ItemwiseForPlot, aes(x = fitness, y = errorRate))
  + geom_point(aes(color = experiment), size = 2)
  + geom_errorbarh(aes(xmax = fitnessUpper, xmin = fitnessLower,
                       color = experiment), 
                  height = 0.01, alpha = .5)
  + geom_errorbar(aes(ymax = errorUpper, ymin = errorLower,
                     color = experiment), 
                width = 0.05, alpha = .5)
  + geom_smooth(method = "lm",colour="black")
  + theme_bw(base_size = 16)
  + theme(aspect.ratio=1)
  + ylab("Error rate")
  + xlab("Distractor fitness / target fitness"))
g
ggsave("~/Repos/keysar_replication/writing/cogsci-revision/images/itemWiseFitness.pdf")
```

@@

>>>>

criticalMessagesExp1 <- read.csv("../experiment1/data/processedLabelsExp1.csv") %>%
  left_join(turkerRatings, by = relevantProperties) %>%
  mutate(exp = "Exp.1")
criticalMessagesExp2 <- read.csv("../experiment2/data/processedLabelsExp2.csv") %>%
  left_join(turkerRatings, by = relevantProperties) %>%
  mutate(exp = "Exp.2")

@@

library(binom)
library(ggthemes)
Exp1Errs = itemInequalitiesExp1 %>%
  do(mutate(., errorLower = binom.confint(.$errorCount, .$total, 
                                     method = "bayes")$lower,
               errorUpper = binom.confint(.$errorCount, .$total, 
                                     method = "bayes")$upper)) %>%
  select(objectSet, errorRate, errorLower, errorUpper)

@@

g <- (ggplot(Exp2ItemwiseForPlot, aes(x = fitness, y = errorRate))
  + geom_point(aes(color = experiment), size = 2)
  + geom_errorbarh(aes(xmax = fitnessUpper, xmin = fitnessLower,
                       color = experiment), 
                  height = 0.01, alpha = .5)
  + geom_errorbar(aes(ymax = errorUpper, ymin = errorLower,
                     color = experiment), 
                width = 0.05, alpha = .5)
  + geom_smooth(method = "lm",colour="black")
  + theme_few(base_size = 16)
  + theme(aspect.ratio=1)
  + ylab("Error rate")
  + xlab("Distractor fitness / target fitness"))
g
ggsave("~/Repos/keysar_replication/writing/cogsci-revision/images/itemWiseFitness.pdf")
```

@@

# Create input for BDA

Create the informativities csv

```{r}
rbind(read_csv('../data/exp1SpeakerLabels.csv') %>% mutate(exp = 'scripted'),
      read_csv('../data/exp2SpeakerLabels.csv') %>% mutate(exp = 'unscripted')) %>%
  mutate(label = str_replace_all(label, fixed(' '), '')) %>%
  mutate(label = str_replace_all(label, "[[:punct:]]", "")) %>% 
  mutate(label = str_to_lower(label, locale = "en")) %>%
  write_csv(path = '../modeling/bdaInput/speakerData.csv')
```
